### 2014-11-12 tex/intro.tex
finished the intro

\item\textbf{-} Show the existence of a bisimulation relation prove
  that the heap summary approach is sound and complete with respect to
  properties provable by GSE.

@@

\noindent{In this paper, we present a brief over of the a Java-like
  language and the encoding of heaps as a bipartiate graph. We use the
  Java-like language to define the formal semantics of the heap
  summary machine and then prove the existence of a bisumulation
  relation. Finally we present an evaluation of the heap summary
  approach. }

>>>>

\item\textbf{-} Show the existence of a bisimulation relation to prove
  that the heap summary approach is sound and complete with respect to
  properties provable by GSE.

@@

\noindent{In this paper, we present a brief overview of a Java-like
  language and the encoding of heaps as a bipartiate graph. We use the
  Java-like language to define the formal semantics of the heap
  summary machine and then prove the existence of a bisumulation
  relation. Finally we present an evaluation of the heap summary
  approach. }
